Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-01-24 SupportingInformation.Rmd
modified with nsd=0.1,1 for standard deviation of noise

model<-"ar1"
fcode<-3

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

```{r cause4copula_stat_ar1_survivalclayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival clayton
model<-"ar1"
fcode<-13

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

@@

model<-"ar1"
fcode<-4

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

```{r cause4copula_stat_ar1_survivalgumbel, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival clayton
model<-"ar1"
fcode<-14

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

@@

model<-"ar1"
fcode<-6

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

```{r cause4copula_stat_ar1_survivaljoe, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival clayton
model<-"ar1"
fcode<-16

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

@@

@@

for(i in rlist){
  params<-c(i,100) # this parameter is a vector with r and K
  p0<-c(params[2],params[2])

@@

  tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_r_",params[1],"_K_",params[2],"_",BiCopName(fcode,short=F),sep="")

@@

# for clayton with spearman and kendall method
  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
}
```

```{r cause4copula_stat_ricker_survivalclayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : clayton

model<-"ricker"
fcode<-13

for(i in rlist){
  params<-c(i,100) # this parameter is a vector with r and K
  p0<-c(params[2],params[2])

@@

# for clayton with spearman and kendall method
  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
}
```

```{r cause4copula_stat_ricker_gumbel, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : clayton

model<-"ricker"
fcode<-4

for(i in rlist){
  params<-c(i,100) # this parameter is a vector with r and K
  p0<-c(params[2],params[2])

@@

# for clayton with spearman and kendall method
  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
}
```

```{r cause4copula_stat_ricker_survivalgumbel, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : clayton

model<-"ricker"
fcode<-14

for(i in rlist){
  params<-c(i,100) # this parameter is a vector with r and K
  p0<-c(params[2],params[2])

@@

# for clayton with spearman and kendall method
  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
}
```

```{r cause4copula_stat_ricker_joe, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : clayton

model<-"ricker"
fcode<-6

for(i in rlist){
  params<-c(i,100) # this parameter is a vector with r and K
  p0<-c(params[2],params[2])

@@

# for clayton with spearman and kendall method
  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
}
```

```{r cause4copula_stat_ricker_survivaljoe, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : clayton

model<-"ricker"
fcode<-16

for(i in rlist){
  params<-c(i,100) # this parameter is a vector with r and K
  p0<-c(params[2],params[2])

@@

# for clayton with spearman and kendall method
  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
}
```
<!--
\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf}
\caption[Comparing noise-copula parameters and estimated population copula parameters with $2500$ sampling points]{Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last \textbf{2500} points for both noise and population data for comparison). p-values $> 0.05$ (above horizontal dashed line) indicate good fit of population copula with same noise cpoula family. \label{fig_Cause4copula_params_GOF_2500}}
\end{center}
\end{figure}

>>>>

model<-"ar1"
fcode<-3
nsd<-1

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

```{r cause4copula_stat_ar1_survivalclayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival clayton
model<-"ar1"
fcode<-13
nsd<-1

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

@@

model<-"ar1"
fcode<-4
nsd<-1

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for gumbel with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for gumbel with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

```{r cause4copula_stat_ar1_survivalgumbel, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival clayton
model<-"ar1"
fcode<-14
nsd<-1

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival gumbel with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for survival gumbel with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

@@

model<-"ar1"
fcode<-6
nsd<-1

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for joe with kendall method only

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for joe with kendall method only

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

```{r cause4copula_stat_ar1_survivaljoe, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival clayton
model<-"ar1"
fcode<-16
nsd<-1

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival joe with kendall method only

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for survival joe with kendall method only

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=nsd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)
```

@@

nsdlist<-c(0.1,1)
Klist<-c(100)

@@

for(insd in nsdlist){
  for(iK in Klist){
   for(i in rlist){
    params<-c(i,iK) # this parameter is a vector with r and K
    p0<-c(params[2],params[2])

@@

    tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_nsd_",insd,"_r_",params[1],"_K_",params[2],"_",BiCopName(fcode,short=F),sep="")

@@

  # for clayton with spearman and kendall method
    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
 }
}
```

```{r cause4copula_stat_ricker_survivalclayton, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival clayton

model<-"ricker"
fcode<-13
nsdlist<-c(0.1,1)
Klist<-c(100)
# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(insd in nsdlist){
  for(iK in Klist){
   for(i in rlist){
    params<-c(i,iK) # this parameter is a vector with r and K
    p0<-c(params[2],params[2])

@@

  # for survival clayton with spearman and kendall method
    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
 }
}
```

```{r cause4copula_stat_ricker_gumbel, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : gumbel

model<-"ricker"
fcode<-4
nsdlist<-c(0.1,1)
Klist<-c(100)
# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(insd in nsdlist){
  for(iK in Klist){
   for(i in rlist){
    params<-c(i,iK) # this parameter is a vector with r and K
    p0<-c(params[2],params[2])

@@

  # for gumbel with spearman and kendall method
    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
 }
}
```

```{r cause4copula_stat_ricker_survivalgumbel, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival gumbel

model<-"ricker"
fcode<-14
nsdlist<-c(0.1,1)
Klist<-c(100)
# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(insd in nsdlist){
  for(iK in Klist){
   for(i in rlist){
    params<-c(i,iK) # this parameter is a vector with r and K
    p0<-c(params[2],params[2])

@@

  # for survival gumbel with spearman and kendall method
    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
 }
}
```

```{r cause4copula_stat_ricker_joe, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : joe

model<-"ricker"
fcode<-6
nsdlist<-c(0.1,1)
Klist<-c(100)
# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(insd in nsdlist){
  for(iK in Klist){
   for(i in rlist){
    params<-c(i,iK) # this parameter is a vector with r and K
    p0<-c(params[2],params[2])

@@

  # for joe with spearman and kendall method

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
 }
}
```

```{r cause4copula_stat_ricker_survivaljoe, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model : survival joe

model<-"ricker"
fcode<-16
nsdlist<-c(0.1,1)
Klist<-c(100)
# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(insd in nsdlist){
  for(iK in Klist){
   for(i in rlist){
    params<-c(i,iK) # this parameter is a vector with r and K
    p0<-c(params[2],params[2])

@@

  # for survival joe with spearman and kendall method

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,nsd=insd,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
 }
}
```
<!--
\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf}
\caption[Comparing noise-copula parameters and estimated population copula parameters with $2500$ sampling points]{Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last \textbf{2500} points for both noise and population data for comparison). p-values $> 0.05$ (above horizontal dashed line) indicate good fit of population copula with same noise cpoula family. \label{fig_Cause4copula_params_GOF_2500}}
\end{center}
\end{figure}
